Data-parallel Training of Neural Networks

### 2019-07-25 paper/paper.tex
EDIT: add author affiliation
EDIT: section structure
Move methodology from implementation to experimental results.
Add subsection to experimental results section.
Remove unused thebibliography section.

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Katharina Flügel}
\IEEEauthorblockA{TODO?}}

@@

\section{Implementation and Methodology} % (fold)
\label{sec:implementation}
We implement and evaluate a synchronous, data-parallel training using MPI-All-Reduce to communicate and aggregate the gradients between different processes.
% TODO: reasons why this technique implemented and not e.g. model parallelism or asynch approaches.

@@

@@

@@

@@

% \begin{thebibliography}{1}
% % TODO
% \end{thebibliography}
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,references}

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Katharina Flügel}
\IEEEauthorblockA{Karlsruhe Institute of Technologie (KIT)\\
katharina.fluegel@student.kit.edu}}

@@

\section{Implementation} % (fold)
\label{sec:implementation}
We implement and evaluate a synchronous, data-parallel training using MPI-All-Reduce to communicate and aggregate the gradients between different processes.
% TODO: reasons why this technique implemented and not e.g. model parallelism or asynch approaches.

@@

\subsection{Methodology} % (fold)
\label{sub:methodology}

The model is trained for a maximum of $20$ (MNIST) or $100$ (CIFAR10) epochs.
The training is stopped if either the maximum number of epochs is reached or if the validation loss could not be improved in the last ten epochs.

After each training epoch, the validation loss is measured.
To compare total training times and speedups, we consider all epochs until the validation loss drops below a certain threshold.
We select a threshold of $0.5$ for MNIST and $1.5$ for CIFAR10.
This threshold is determined by rounding up the maximum of the minimal validation loss for each training on that dataset.

% subsection methodology (end)

\subsection{Impact of the batch size} % (fold)
\label{sub:impact_of_the_batch_size}

@@

% subsection impact_of_the_batch_size (end)

\subsection{Communication Time} % (fold)
\label{sub:communication_time}

@@

% subsection communication_time (end)

\subsection{Speedup} % (fold)
\label{sub:speedup}

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,references}
